FraCaS: Temporal Analysis

### 2020-06-22 paper2020/paper.tex
conclusions

Another issue to be looking at is the codification of lexical
aspect.\todo{update} In what we have been doing so far, we did not distinguish
between the present continuous and the present or the simple past and
the past continuous and their interaction with non-lexical aspect.
The main reason for this is that in the test suite, even though there
are examples of inferences based on the either lexical or non-lexical
aspect, no example where an interaction between the two exists. For
example, one such case is the one shown below and exemplifies the
difference between activities and accomplishments with respect to the
different inferences they give when used in the past continuous:

\fracasex{extra1}{
	\item	John was writing a book. 
	\hyp 	John wrote a book (UNK).
}

\fracasex{extra2}{
	\item	John was running. 
	\hyp 	John ran (YES).
}

\fracasex{extra1}{
	\item	John wrote a book. 
	\hyp 	John was writing a book (YES).
}

\fracasex{extra2}{
	\item	John ran.
	\hyp 	John was running (YES?).
}

>>>>

Another thing we would be willing to try is an extension of the FraCaS test suite that will include more fine-grained examples of lexical and grammatical aspect and  the interaction between those two, for example cases where one needs to actually distinguish between achievements and accomplishments on the basis of their inferential properties:

\fracasex{extra1}{
	\item	John found his keys.  
	\hyp 	John was finding his keys  (UNK).
}

\fracasex{extra2}{
	\item	John wrote a book.  
	\hyp 	John was writing a book  (YES).
}

In the first of the two examples involving an achievement verb, the inference is UNK, since there is no guarantee that the action is non-instanteous. To the contrary, for accomplishment verbs, the inference follows.

Further cases to be included in an extended FraCaS future suite involve examples where the interaction between different tenses needs to be captured:
%Another issue to be looking at is the codification of lexical
%aspect.\todo{update} In what we have been doing so far, we did not distinguish
%between the present continuous and the present or the simple past and
%the past continuous and their interaction with non-lexical aspect.
%The main reason for this is that in the test suite, even though there
%are examples of inferences based on the either lexical or non-lexical
%aspect, no example where an interaction between the two exists. For
%example, one such case is the one shown below and exemplifies the
%difference between activities and accomplishments with respect to the
%different inferences they give when used in the past continuous:

\fracasex{extra3}{
	\item	When the phone rang, John had entered the house.  
	\hyp 	John entered the house before the phone rang (YES).
}
